Delocalization of Eigenvectors in Random Matrices

### 2025-03-22 Draft.tex
movez

$$F(H_{ij}) = F(H_{11}^G, \cdots, H_{i, j-1}^G, tH_{ij}, H_{i, j+1}, \cdots H_{NN})$$
 By the chain rule: $$\partial_t F(tH_{ij}) = \partial_{H_{ij}} F(tH_{ij})H_{ij} + \partial_{H_{ji}} F(tH_{ij})\overline{H_{ij}}$$
(\textcolor{red}{prove by induction? - also justify the first formula} - Similarly, we have: 
$$\frac{d^k}{dt^k} F(tH_{ij}) = \sum_{k=0}^k c_{\ell, k}\partial_{H_{ij}}^\ell \partial_{H_{ji}}^{k-\ell} F(tH_{ij})H_{ij}^\ell \left(\overline{H_{ij}}\right)^{k-\ell}$$

>>>>

$$F(tH_{ij}) = F(H_{11}^G, \cdots, H_{i, j-1}^G, tH_{ij}, H_{i, j+1}, \cdots H_{NN})$$
 By the chain rule: $$\partial_t F(tH_{ij}) = \partial_{H_{ij}} F(tH_{ij})H_{ij} + \partial_{H_{ji}} F(tH_{ij})\overline{H_{ij}}$$
(\textcolor{red}{prove by induction? - also justify the first formula} - Similarly, we have: 
$$\frac{d^k}{dt^k} F(tH_{ij}) = \sum_{k=0}^k c_{\ell, k}\partial_{H_{ij}}^\ell \partial_{H_{ji}}^{k-\ell} F(tH_{ij})H_{ij}^\ell \left(\overline{H_{ij}}\right)^{k-\ell}$$
